The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-03-22 repeater-vladata.tex
reasonable spectral and rate discussion sections

\section{discussion}
\label{sec:disc}
\subsection{Burst Spectra}
We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz. At the same time, three other bursts had similar observing coverage but were not detected simultaneously. Given that the Arecibo detection is an order of magntude weaker than the VLA detection and that multiple VLA bursts appear largely within the 3~GHz band, we conclude that \frb\ burst spectra are not well described by a powerlaw. Instead, bursts spectrally are well-described by a Gaussian-like shape with a 500~MHz-scale envelope. This is consistent with \citet{WEIRD}, which uses high-resolution Arecibo spectra to identify rich spectral structure ("sub-bursts") intrinsic to each burst.

After correcting for barycentric and typical dispersion delays, the VLA/Arecibo burst spectrum shows a residual temporal drift. This drift can be interpreted as an excess DM of roughly 5 pc cm$^{-3}$. This excess DM is similar in size to the burst-to-burst variation in DM measured for the whole sample of VLA 3~GHz bursts and had been noted in earlier 1.4~GHz Arecibo observations of \frb \citep{2016arXiv160308880S}. The VLA bursts demonstrate that this ''excess'', burst-specific DM is seen up to 3~GHz. The simultaneous VLA/Arecibo burst shows that the (instantaneous) burst properties from 1.2 to 3.5~GHz are consistent with a single excess.

These features are generally consistent with intrinsic burst properties described in \citet{WEIRD}. That work uses bright, coherently-dedispersed bursts to define a heuristic that distinguishes between burst-specific and time-stationary dispersion-like effects. They show that the bursts are composed of "sub-bursts" that preferentially drift to lower frequencies at later times, which systematically biases DM measurements that maximize S/N ratio. Interestingly, our MCMC modeling of the VLA bursts shows a weak correlation between larger apparent DM and pulse width. This could be a signature of blending of many unresovled sub-bursts in a single VLA burst spectrum. Assuming a long-term average DM of 560.5 pc cm$^{-3}$, we can ascribe the observed excess DM to an intrinsic burst drift rate measured on the order of $\sim100$~MHz/ms.

@@

\subsection{Energy and Flux Distribution}
The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg. We now know that \frb\ is detectable with the VLA out to $z=0.7$. \frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}. While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any known Galactic radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.

In \S \ref{sec:disn} we compare the energy distribution of the 9 VLA bursts to those reported earlier by Arecibo and the GBT. In all cases, bursts are detected over a wide range of significance that is indicative of a relatively flat distribution. All three energy distributions can be characterized as a powerlaw in $dN/dE$ with slope $\sim-1.7$. This slope is seen even though the burst rate varies by almost an order of magnitude between observations and frequencies cover both 1.4 and 3~GHz bands. This suggests that the slope is related to the underlying physical process, rather than the state at any given time. The value of the energy distribution slope is similar to that observed in X-ray fluxes of solar flares \citep{2011SoPh..274...99A} and gamma-ray fluence of bursts from soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}. In these cases, the value of the slope is close to the theoretical expectation for self-regulated critical phenomena \citep[slope$=-5/3$;][]{2011SoPh..274...99A}.

This work expands the redshift horizon for detectability of \frb, suggesting that cosmological effects are even more important for understanding properites of the FRB population. An early observable property of the FRB population is the flux distribution, $dN/dF \propto F^{\alpha}$. For a uniform distribution of sources, the powerlaw index, $\alpha$, takes on the special value of --1.5 \citep[the ''Euclidean distribution'';][]{2016MNRAS.462..941L}. Deviations from the Euclidean distribution have been used to suggest that GRBs were indeed a cosmological distribution. Multiple studies have suggested that FRBs have a ''flat'' flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}, although others have cautioned that a powerlaw distribution is an approximation that can confuse any meaningful inferences \citep{2017arXiv170208040C}.

\citet{2017arXiv170208040C} describe show how the measured flux distribution is sensitive to the maximum distance...
FRB detections have often been far brighter than the limiting brightness of telescopes detecting them \citep{2007Sci...318..777L, 2016arXiv161105758R}. 
This is well known in the study of GRBs, which used the $V/V_{\rm{max}}$\ test (ratio of maximum to limiting brightness) to first infer that that population was cosmological \citep{1992ApJ...388L..45M}.

Effects relevant to FRBs:
- redshift space distortion
- time dilation (rate calculation correction scales as $1+z$)
- frequency-dependent FRB rate
All tend to flatten the $dN/dF$\ distribution with increasing z.

The VLA and Arecibo observed intensively during the late-2016 campaign, but a complete search for bursts from the Arecibo is ongoing. Soon we will be able to calculate a frequency-dependent burst rate, but early results suggest that the burst rate at a fixed energy is much higher at 1.4~GHz than at 3~GHz. If so, we should expect an additional redshift-dependent effect that will flatten the $dN/dF$\ distribution.

@@

\subsection{Repetition}
The burst rate analysis presented in \S \ref{sec:temp} shows that the detection probability of \frb\ is not stationary. As mentioned above, this could be caused by intrinsic events (e.g., magnetar outburst) or propagation effects. While a detailed analysis of temporal correlation will require more bursts and/or more sophistication, it is clear that \frb\ has significant correlation on short timescales \citep[sometimes called a ``red spectrum'';][]{2016MNRAS.458L..89C}. Another way of stating this is that the detection of a burst improves odds of finding more bursts in near-future observations.

@@

\subsection{Observing Strategies}
As discussed above, \citet{2016MNRAS.458L..89C} note that the FRB repetition implies that the number of FRB-generating sources is smaller than implied by the number of bursts. In some scenarios, this means that there are areas on the sky that may contain no FRBs. Wide, shallow surveys are the preferred strategy for blind detection of FRBs. However, future efforts to localize FRBs are still most likely to succeed by targeting known FRBs to catch repetitions, assuming that all FRBs repeat. Finally, we note that the average spectral coverage of bursts from \frb\ are relatively narrow ($<1$~GHz) and the coverage changes dramatically between bursts. Thus, the odds of detecting a burst will improve linearly with bandwidth for bandwidths wider than this characteristic scale.

Studying a cosmological source population will require making redshift corrections. The limited envelope of bursts from \frb\ suggest that spectral extrapolations based on a spectral index are not likely to be reliable. It is more reasonable to treat the FRB rate as a frequency-dependent property, than to scaling from a single rate via a spectral index.

burst rate is correlated between vla and ao, but not the intensity of individual bursts...

>>>>

\section{discussion}
\label{sec:disc}
\subsection{Burst Spectra}

We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz. The Arecibo burst flux density is an order of magntude less than that seen by the VLA. At the same time, three other bursts from \frb\ had similar observing coverage but were not detected simultaneously. This is consistent with the spectral structure observed within the 3~GHz VLA band, which is typically limited to a Gaussian envelope with width of roughly 500~MHz. The center frequency of this envelope is a unique property of each burst and does not show an obvious pattern between bursts.

If \frb\ burst spectra are typical of the larger FRB population, then population models need to be generalized beyond the assumption of a spectral powerlaw. Most obviously, \frb\ implies that future multi-telescope searches for bursts are unlikely to simultaneously detect bursts in different bands. Second, since burst spectra have limited bands, the burst detection rate at one frequency may not represent that at another. That will require rate estimates for the FRB population to be made explicitly frequency-dependent. Finally, we note that the odds of detecting a burst will improve with bandwidth for bandwidths wider than their characteristic scale.

After correcting for barycentric and typical dispersion delays, the VLA/Arecibo burst spectrum shows a residual temporal drift. This drift can be interpreted as an excess DM of roughly 5 pc cm$^{-3}$. We also measure a burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts of a similar scale. This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this ''excess'', burst-specific DM is seen up to 3~GHz. The simultaneous VLA/Arecibo burst also shows that an individual burst's properties from 1.2 to 3.5~GHz are consistent with a single excess.

These features are generally consistent with intrinsic burst properties described in \citet{WEIRD}. That work uses bright, coherently-dedispersed bursts to identify ''sub-bursts'' that preferentially drift to lower frequencies at later times. With high-resolution dynamic spectra, one can define a heuristic that distinguishes between a burst-specific dispersion-like effect and a more stable (''true'') dispersion. Since the sub-bursts tend to drift to lower frequencies, they systematically bias DM measurements made with low-resolution data (like the VLA and earlier Arecibo and GBT obsrevaitons). Interestingly, our modeling of the VLA burst dynamic spectra show a weak correlation between larger apparent DM and pulse width. This could be a signature of blending of many unresovled sub-bursts in a single VLA burst spectrum.

@@

\subsection{Energy and Flux Distribution}

The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg. \frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}. 
%While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any known Galactic radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.

In \S \ref{sec:disn} we compare the energy distribution of the 9 VLA bursts to those reported earlier by Arecibo and the GBT. All three energy distributions can be characterized as a powerlaw in $dN/dE$ with slope $\sim-1.7$. This slope is seen even though the burst rate varies by almost an order of magnitude between observations and frequencies cover both 1.4 and 3~GHz bands. This suggests that the slope is related to the underlying physical process, rather than the state at any given time. The value of the energy distribution slope is similar to that observed in gamma-ray fluence of bursts from soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}. This similarity has been used to argue that bursts are driven by self-regulated critical phenomena \citep[slope$=-5/3$;][]{2011SoPh..274...99A}.

While the surprising brightness of new FRB discoveries was once seen as a cause for concern (i.e., a sign of terrestrial interference), we may be able to use this to infer properties of the overall population \citep{2007Sci...318..777L, 2016arXiv161105758R}. When modeling the flux distribution as a powerlaw, an isotropic distribution of sources will have a powerlaw index, $\alpha$, of --1.5 \citep[the ''Euclidean distribution'';][]{2016MNRAS.462..941L}. Prior to the measurement of the first GRB redshift, deviations from the Euclidean distribution were used to infer their cosmological distribution \citep[e.g., the $V/V_{\rm{max}}$\ test;][]{1992ApJ...388L..45M, 1995ApJ...453...25F}. Multiple studies have suggested that FRBs have a ''flat'' flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. Others have noted that the flux distribution is not well modeled as a powerlaw, such that $\alpha$\ is effectively sensitivity (and telescope) dependent \citep{2016MNRAS.461..984O, 2017arXiv170208040C}.

We now know that \frb\ is detectable with the VLA out to $z=0.7$, which suggests that cosmological effects are even more important for understanding properites of the FRB population. \citet{2017arXiv170208040C} demonstrate how redshift space distortions, time dilation, and spectral index (''k-correction'') effects can flatten the flux distribution. To this complex scene, we add the fact that \frb\ burst spectra are not defined by a spectral index, which suggests that k-corrections are likely to be very difficult to calculate in practice. Rather than using wide band burst spectra to measure a single ''typical'' spectral index, we now must measure the burst rate as a function of frequency. These need not be measured simultaneously, but rather contemporaneously to insure they represent a similar state of activitity of the FRB.

If we assume \frb\ is representative of the FRB population, we can estimate this frequency-dependent burst rate. The VLA and Arecibo observed intensively in a coordinated fashion during the late-2016 campaign. A complete search for bursts from the Arecibo is ongoing, but early results suggest that the burst rate at a fixed energy is much higher at 1.4~GHz than at 3~GHz. This suggests that high-redshift FRBs will have an apparently lower rate that flattens the $dN/dF$\ distribution in a manner similar to a k-correction. We can only infer the presence of this effect for observations near 1.4~GHz, since we have no estimate of the \frb\ burst rate outside the frequency range from 1.4 to 3~GHz. Propagation effects suggest that the rate will be lower at sub-GHz frequencies \citep{2017MNRAS.465.2286R}. If so, the tension between constraints on $\alpha$\ near 800~MHz and 1.4~GHz may be resolved by a frequency-dependent FRB rate that peaks near 1.4~GHz.

@@

\subsection{Repetition}

The burst rate analysis presented in \S \ref{sec:temp} shows that the detection probability of \frb\ is not stationary. As mentioned above, this could be caused by intrinsic events (e.g., magnetar outburst) or propagation effects. While a detailed analysis of temporal correlation will require more bursts and/or more sophistication, it is clear that \frb\ has significant correlation on short timescales \citep[sometimes called a ``red spectrum'';][]{2016MNRAS.458L..89C}. Another way of stating this is that the detection of a burst improves odds of finding more bursts in near-future observations.

@@

\subsection{Observing Strategies}
As discussed above, \citet{2016MNRAS.458L..89C} note that the FRB repetition implies that the number of FRB-generating sources is smaller than implied by the number of bursts. In some scenarios, this means that there are areas on the sky that may contain no FRBs. Wide, shallow surveys are the preferred strategy for blind detection of FRBs. However, future efforts to localize FRBs are still most likely to succeed by targeting known FRBs to catch repetitions, assuming that all FRBs repeat.
